### 2020-08-08 factor.Rmd
targets and draft manuscript complete

---
title: Development of the Nursing Confidence in Managing Sedation Complications
  Scale (NC-MSCS)
output:
  html_notebook: default
  pdf_document: default
  word_document: default
---

#Introduction
Prompt detection and initiation of appropriate treatment for sedation-related complications is vital to ensure patient safety during nurse-administered procedural sedation and analgesia (PSA). People will exert maximal effort and persist despite failure if they believe they are capable in completing a given task. It is possible that nurses may not take necessary actions to manage sedation-related complications if they lack confidence in their abilities to complete the task. The aim of this study was to develop and validate the nursing confidence in managing sedation complications scale (NCMSCS).

#Methods
A draft version of the NC-MSCS was developed from clinical practice guidelines. An expert panel of nurses and medical practitioners who have expertise in anaesthesia or PSA were asked to rate the relevance of each item. Items with a content validity index of less than 0.78 were revised and those with very low index values were deleted. To evaluate the psychometric properties of the revised scale, an online survey was distributed to nurses who were members of operating theatre, endoscopy, cardiac cath lab, radiology and critical care specialty nursing associations. Exploratory factor analysis was undertaken to provide evidence of the structural validity of the scale.

*Load data*

```{r}
load("data/data.Rdata")
```

##Descriptive statistics for the sample
```{r}
library(psych)
data$GSES=rowMeans(data[,14:21], na.rm = TRUE)
variables=c(7:9,22:23,58)
kableExtra::kable(describe(data[,variables]), caption="Descriptive statistics")
##need to also add in factor variable descriptives.
``` 
##Missing data analysis

```{r}
df=data[,24:57]
```

The percent of missing data:
```{r}
(sum(is.na(df))/prod(dim(df)))*100
```

Impute with expectation maximisation

```{r}
library(TestDataImputation)
df1=EMimpute(df, Mvalue = "NA", max.score = 7)
```

*Prepare dataframe for exploratory factor analysis*
Delete items:
Sedation reversal – worded with more than one part in the question
Laryngeal mask airway – not all trained for this
AssessLevel Sedation - wording was too similar to identify over-sedation

```{r}
df1$Medication=NULL
df1$LMA=NULL
df1$AssessLevelSedation=NULL
```

```{r}
describe(df1)
```

```{r}
summary(df1)
```

*Box plots of item distributions from https://towardsdatascience.com/a-gentle-guide-to-statistics-in-r-ccb91cc1177e*

```{r}
library(tidyr)
#create long dataframe
dflong=gather(df1,key=Item, value=Confidence)
#Change item names
library(plyr)
dflong$Item=mapvalues(dflong$Item, from = c("RiskHistory" ,        "RiskOSA"       ,          "DifficultIntubate"    ,   "DifficultBMV"           
,"RiskASA"        ,            "RiskBMI"          ,       "RiskCardioresp",
"IdentifyHypoventilation", "IdentifyRespRate"    ,    "IdentifyAllergy"  ,
 "IdentifyBradycardia"   ,  "IdentifyHypotension"     ,         "RespondHypoventilation" ,
 "RespondHypoxia"      ,      "RespondBradycardia"    ,  "RespondHypotension" ,
"NontechAssess"  ,"NontechAccessAssist","NontechRespond",
"OPA"     ,                "NPA"          ,           "JawSupport"  ,           
"ChinLift", "BMV", "IdentifyLaryngospasm", "IdentifyObstruction", "IdentifyOversedation", "NontechIdentifyAssist", "RespondObstruction", "RiskComorbid", "RiskFrailty"), to = c("Assess risk from anaesthetic history" ,        "Assess risk from sleep apnoea"       ,          "Determine risk for difficult intubation"    ,   "Determine risk for difficult bag mask ventilation"           
,"Assess risk from ASA classification status"        ,            "Assess risk from body mass index"          ,       "Assess risk from cardiorespiratory reserve",
"Identify hypoventilation", "Identify abnormal respiratory rate"    ,    "Identify allergic reactions"  ,
 "Identify bradycardia"   ,  "Identify hypotension"     ,         "Respond to hypoventilation" ,
 "Respond to hypoxia"      ,      "Respond to bradycardia"    ,  "Respond to hypotension" ,
"Cease procedure to assess patient"  ,"Cease procedure to gain extra assistance","Cease procedure to treat complication",
"Insert oropharyngeal airway"     ,                "Insert nasopharyngeal airway"          ,           "Apply jaw support"  ,           
"Apply chin lift", "Perform bag-mask ventilation", "Identify laryngospasm", "Identify airway obstruction", "Identify oversedation", "Identify when extra assistance required", "Respond to airway obstruction", "Assess risk from comorbidities", "Assess risk from frailty assessment"))
library(ggplot2)
ggplot(data = dflong, # add the data
       aes(x = Item, y = Confidence, # set x, y coordinates
           color = Item)) +    # color by item
  geom_boxplot() +
theme(axis.ticks = element_blank(), axis.text.x = element_blank())
```

##Test factorability using KMO

```{r}
KMO(df1)
```

## Determine Number of Factors to Extract
```{r}
library(nFactors)
polycor=polychoric(df1, smooth = FALSE)
ev <- eigen(cor(polycor$rho))
ap <- parallel(subject=nrow(polycor$rho),var=ncol(polycor$rho),
  rep=100,cent=.05, model="factors")
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

##Exploratory factor analysis

###Trial of 3 factors

```{r}
df3=df1
polycor=polychoric(df3, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Conceptualise factor structure as:
1. a factor for assessing risk of and identification of airway complications
2. A factor for treating airway complications
3. Other complications

Remove RiskComorbidity because difference <0.15

```{r}
df3$RiskComorbid=NULL
polycor=polychoric(df3, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove IdentifyHypoventilation becuase difference <0.15

```{r}
df3$IdentifyHypoventilation=NULL
polycor=polychoric(df3, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove BMV as difference <0.15

```{r}
df3$BMV=NULL
polycor=polychoric(df3, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove RespondObstruction because difference <0.15

```{r}
df3$RespondObstruction=NULL
polycor=polychoric(df3, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove RiskFrailty because it loaded on the wrong factor

```{r}
df3$RiskFrailty=NULL
polycor=polychoric(df3, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove NontechAccessAssist because of Heywood case

```{r}
df3$NontechAccessAssist=NULL
polycor=polychoric(df3, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

This solution identified a factor structure consisting of:
1. Advanced airway assessment skills
2. Technical skills related to airway patency
3. General skills related to identifying and responding to sedation-related complications.

##Create scale and subscale scores for 3 factor solution

```{r}
MSCS.keys.3=list(advanced=c("RiskHistory" ,        "RiskOSA"       ,          "DifficultIntubate"    ,   "DifficultBMV"           
,"RiskASA"        ,            "RiskBMI"          ,       "RiskCardioresp", "IdentifyLaryngospasm", "IdentifyObstruction"),
general=c("IdentifyRespRate"    ,    "IdentifyAllergy"  , "IdentifyOversedation",
 "IdentifyBradycardia"   ,  "IdentifyHypotension"     ,         "RespondHypoventilation" ,
 "RespondHypoxia"      ,      "RespondBradycardia"    ,  "RespondHypotension" ,"NontechAssess"  ,"NontechIdentifyAssist","NontechRespond"  ),
airway=c("OPA"     ,                "NPA"          ,           "JawSupport"  ,           
"ChinLift" ),
total=c("RiskHistory" ,        "RiskOSA"       ,          "DifficultIntubate"    ,   "DifficultBMV"           
,"RiskASA"        ,            "RiskBMI"          ,       "RiskCardioresp", "IdentifyLaryngospasm", "IdentifyObstruction", "IdentifyOversedation",
 "IdentifyRespRate"    ,    "IdentifyAllergy"  ,
 "IdentifyBradycardia"   ,  "IdentifyHypotension"     ,         "RespondHypoventilation" ,
 "RespondHypoxia"      ,      "RespondBradycardia"    ,  "RespondHypotension" ,
"NontechAssess"  ,"NontechAccessAssist","NontechRespond",
"OPA"     ,                "NPA"          ,           "JawSupport"  ,           
"ChinLift"))
```

```{r}
my.scales.3=scoreItems(MSCS.keys.3, df1)
my.scores.3=my.scales.3$scores
```

Add scale scores to data frame

```{r}
data$advanced=my.scores.3[,1]
data$general=my.scores.3[,2]
data$airway=my.scores.3[,3]
data$total.3=my.scores.3[,4]
```

Describe scale scores

```{r}
plyr::count(data$advanced)
plyr::count(data$airway)
plyr::count(data$general)
plyr::count(data$total.3)
```

*Start of alternative 3 factor solution: Remove RiskFrailty because it loaded on the wrong factor*

```{r}
df3alt=df1
df3alt$RiskFrailty=NULL
polycor=polychoric(df3alt, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove RiskComorbid because difference <0.15

```{r}
df3alt$RiskComorbid=NULL
polycor=polychoric(df3alt, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove IdentifyLaryngospasm because it loaded on the wrong factor
```{r}
df3alt$IdentifyLaryngospasm=NULL
polycor=polychoric(df3alt, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove IdentifyObstruction because it loaded on the wrong factor

```{r}
df3alt$IdentifyObstruction=NULL
polycor=polychoric(df3alt, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove IdentifyHypoventilation because difference was <0.15

```{r}
df3alt$IdentifyHypoventilation=NULL
polycor=polychoric(df3alt, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

Remove RespondHypoventilation because difference was <0.15

```{r}
df3alt$RespondHypoventilation=NULL
polycor=polychoric(df3alt, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 3, rotate = "Promax", fm="ols")
factor
```

###Trial of 4 factor structure

```{r}
df4=df1
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove IdentifyLaryngospasm because it loaded highly on the wrong factor

```{r}
df4$IdentifyLaryngospasm=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove RiskFrailty because it loaded on wrong factor*

```{r}
df4$RiskFrailty=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove RespondObstruction – loaded on more than one factor with difference <0.15*

```{r}
df4$RespondObstruction=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove RiskComorbidity because it loaded highly on two factors with difference <0.15 between factors*

```{r}
df4$RiskComorbid=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove Identifyobstruction – loaded on wrong factor*

```{r}
df4$IdentifyObstruction=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove NontechIdentifyAssist because loaded highly on two factors with <0.15 difference*

```{r}
df4$NontechIdentifyAssist=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove BMV loaded less than 0.4 on all factors*

```{r}
df4$BMV=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "Promax", fm="ols")
factor
```

Remove IdentifyOversedation loaded less than 0.4 on all factors*

```{r}
df4$IdentifyOversedation=NULL
polycor=polychoric(df4, smooth = FALSE)
factor=fa(polycor$rho, nfactors = 4, rotate = "promax", fm="ols")
```

```{r}
print(factor)
```

## Create scale and subscale scores

```{r}
MSCS.keys=list(risk=c("RiskHistory" ,        "RiskOSA"       ,          "DifficultIntubate"    ,   "DifficultBMV"           
,"RiskASA"        ,            "RiskBMI"          ,       "RiskCardioresp"),
identify=c("IdentifyHypoventilation", "IdentifyRespRate"    ,    "IdentifyAllergy"  ,
 "IdentifyBradycardia"   ,  "IdentifyHypotension"     ,         "RespondHypoventilation" ,
 "RespondHypoxia"      ,      "RespondBradycardia"    ,  "RespondHypotension"   ),
nontech=c("NontechAssess"  ,"NontechAccessAssist","NontechRespond" ),
tech=c("OPA"     ,                "NPA"          ,           "JawSupport"  ,           
"ChinLift" ),
total=c("RiskHistory" ,        "RiskOSA"       ,          "DifficultIntubate"    ,   "DifficultBMV"           
,"RiskASA"        ,            "RiskBMI"          ,       "RiskCardioresp",
"IdentifyHypoventilation", "IdentifyRespRate"    ,    "IdentifyAllergy"  ,
 "IdentifyBradycardia"   ,  "IdentifyHypotension"     ,         "RespondHypoventilation" ,
 "RespondHypoxia"      ,      "RespondBradycardia"    ,  "RespondHypotension" ,
"NontechAssess"  ,"NontechAccessAssist","NontechRespond",
"OPA"     ,                "NPA"          ,           "JawSupport"  ,           
"ChinLift"))
```

```{r}
my.scales=scoreItems(MSCS.keys, df1)
my.scores=my.scales$scores
```

Add scale scores to data frame

```{r}
data$risk=my.scores[,1]
data$identify=my.scores[,2]
data$nontech=my.scores[,3]
data$tech=my.scores[,4]
data$total=my.scores[,5]
```

###Describe scale scores

```{r}
plyr::count(data$tech)
plyr::count(data$nontech)
plyr::count(data$risk)
plyr::count(data$identify)
plyr::count(data$total)
plyr::count(data$OverallConfidence)
describe(data[,58:62])
```

*Plot from: https://rpubs.com/danmirman/plotting_factor_analysis*
```{r}

t=as.table(print(factor$loadings))
t1=as.data.frame(t)
library(plyr)
t1$Var2=mapvalues(t1$Var2, from = c("A", "B", "C", "D"), to = c("Identify and respond", "Risk assessment", "Technical skills", "Non-technical skills"))
t1$Var1=mapvalues(t1$Var1, from = c("RiskHistory" ,        "RiskOSA"       ,          "DifficultIntubate"    ,   "DifficultBMV"           
,"RiskASA"        ,            "RiskBMI"          ,       "RiskCardioresp",
"IdentifyHypoventilation", "IdentifyRespRate"    ,    "IdentifyAllergy"  ,
 "IdentifyBradycardia"   ,  "IdentifyHypotension"     ,         "RespondHypoventilation" ,
 "RespondHypoxia"      ,      "RespondBradycardia"    ,  "RespondHypotension" ,
"NontechAssess"  ,"NontechAccessAssist","NontechRespond",
"OPA"     ,                "NPA"          ,           "JawSupport"  ,           
"ChinLift"), to = c("Assess risk from anaesthetic history" ,        "Assess risk from sleep apnoea"       ,          "Determine risk for difficult intubation"    ,   "Determine risk for difficult bag mask ventilation"           
,"Assess risk from ASA classification status"        ,            "Assess risk from body mass index"          ,       "Assess risk from cardiorespiratory reserve",
"Identify hypoventilation", "Identify abnormal respiratory rate"    ,    "Identify allergic reactions"  ,
 "Identify bradycardia"   ,  "Identify hypotension"     ,         "Respond to hypoventilation" ,
 "Respond to hypoxia"      ,      "Respond to bradycardia"    ,  "Respond to hypotension" ,
"Cease procedure to assess patient"  ,"Cease procedure to gain extra assistance","Cease procedure to treat complication",
"Insert oropharyngeal airway"     ,                "Insert nasopharyngeal airway"          ,           "Apply jaw support"  ,           
"Apply chin lift"))
names=c("Item", "Factor", "Loading")
colnames(t1)=names

library(ggplot2)
#For each test, plot the loading as length and fill color of a bar
# note that the length will be the absolute value of the loading but the 
# fill color will be the signed value, more on this below

ggplot(t1, aes(Item, abs(Loading), fill=Loading)) + 
  facet_wrap(~ Factor, nrow=1) + #place the factors in separate facets
  geom_bar(stat="identity") + #make the bars
  coord_flip() + #flip the axes so the test names can be horizontal  
  #define the fill color gradient: blue=positive, red=negative
  scale_fill_gradient2(name = "Loading", 
                       high = "blue", mid = "white", low = "red", 
                       midpoint=0, guide=F) +
  ylab("Loading Strength") + #improve y-axis label
  theme_bw(base_size=10) #use a black and white theme with set font size

```

##Test construct validity through multiple regression of factors potentially associated with confidence in managing sedation-related complications

Create total general self efficacy scale score

```{r}
data$GSE=rowSums(data[,14:21], na.rm = FALSE)
head(data$GSE)
```

Create critical care dummy variable

```{r}
data$critcare=data$Specialty==10|data$Specialty==9|data$Specialty==8|data$Specialty==7
```

Load the broom, dplyr and kableExtra packages

```{r}
library(broom)
library(kableExtra)
library(dplyr)
```

Model for total score 
```{r}
model=lm(total~YearsNursing+ PSAFrequency+ YearsPSA+ ALS+ PSAEducation+ GSE+ critcare+ PSAPolicy+ Competency+ OverallKnowledge, data)
kable(tidy(model, conf.int=TRUE))
```

Plot

```{r}
ggplot(tidy(model, conf.int=TRUE), aes(estimate, term, color = term)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) +
  geom_vline(aes(xintercept=0))+
  scale_y_discrete(labels = c("(Intercept)", "ALS", "Unit has a PSA Competency", "Critical care", "General self-efficacy", "Sedation knowledge rating", "Education", "Frequency using PSA", "Unit has a PSA Policy", "Years Nursing", "Years administering sedation")) +
  theme(legend.position="none")+
  labs(y = "Predictor", x="Estimate") + 
  theme(axis.title.y = element_text(size = 14, face = "bold"), axis.title.x = element_text(size = 14, face = "bold"))+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank())
```

ggcoefstats plot

https://cran.r-project.org/web/packages/ggstatsplot/vignettes/ggcoefstats.html

Model for risk assessment scale 
```{r}
model=lm(data$risk~data$YearsNursing+data$PSAFrequency+data$YearsPSA+data$ALS+data$PSAEducation+data$GSE+data$critcare+data$PSAPolicy+data$Competency + data$OverallKnowledge)
summary(model)
```

Model for identifying and responding to complications scale 
```{r}
model=lm(data$identify~data$YearsNursing+data$PSAFrequency+data$YearsPSA+data$ALS+data$PSAEducation+data$GSE+data$critcare+data$PSAPolicy+data$Competency+ data$OverallKnowledge)
summary(model)
```

Model for technical skills scale 
```{r}
model=lm(data$tech~data$YearsNursing+data$PSAFrequency+data$YearsPSA+data$ALS+data$PSAEducation+data$GSE+data$critcare+data$PSAPolicy+data$Competency+ data$OverallKnowledge)
summary(model)
```

Model for non-technical skills scale 
```{r}
model=lm(data$nontech~data$YearsNursing+data$PSAFrequency+data$YearsPSA+data$ALS+data$PSAEducation+data$GSE+data$critcare+data$PSAPolicy+data$Competency+ data$OverallKnowledge)
summary(model)
```

*consider doing plots of multiple regressions using ggstatsplot:: ggcoefstats*
https://cran.r-project.org/web/packages/ggstatsplot/vignettes/ggcoefstats.html

*plots for associations between total scores and explanatory variables*

```{r}
ggplotRegression <- function (fit) {

  library(ggplot2)

  ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
    geom_point() +
    theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
    stat_smooth(method = "lm", col = "red") +
    labs(title = paste("Adj R squared = ",signif(summary(fit)$adj.r.squared, 5),
                       "Intercept =",signif(fit$coef[[1]],5 ),
                       " Slope =",signif(fit$coef[[2]], 5),
                       " P =",signif(summary(fit)$coef[2,4], 5)))
}

ggplotRegression(lm(total ~ OverallConfidence, data = data))
ggplotRegression(lm(total ~ OverallKnowledge, data = data))
ggplotRegression(lm(total ~ YearsPSA, data = data))
ggplotRegression(lm(total ~ YearsNursing, data = data))
ggplotRegression(lm(total ~ PSAFrequency, data = data))
ggplotRegression(lm(total ~ GSE, data = data))
```

*Reliability analysis*
```{r}
reliability.total=psych::alpha(df1)$total$std.alpha

dfnontech=data.frame(data$NontechAccessAssist, data$NontechRespond, data$NontechAssess)
reliability.nontech=psych::alpha(dfnontech)$total$std.alpha

dftech=data.frame(data$ChinLift, data$JawSupport, data$NPA, data$OPA)
reliabilitytech=psych::alpha(dftech)$total$std.alpha

dfrisk=data.frame(df1[,1:7])
reliabilityrisk=psych::alpha(dfrisk)$total$std.alpha

dfidentify=data.frame(df1[,c(8:12,14:17)])
reliability.identify=psych::alpha(dfidentify)$total$std.alpha
data.frame(reliability.total,reliability.identify,reliability.nontech, reliabilitytech, reliabilityrisk)
```

##Responsiveness

Load data

```{r}
responsiveness <- readr::read_csv("data/responsiveness.csv")
```

Create pre NC-MSCS scores

Print variable pre-test variable names
```{r}
names.list=names(responsiveness)
```

Print variable pre-test variable names
```{r}
variablenames.mscsPost=dput(grep(".post$", names(responsiveness), value=TRUE))
names.list[29:30]
```

```{r}

pre.keys=list(risk=c("Risk_anaesthesia_pre", "Risk_OSA_pre" ,          "Risk_intubate_pre"     ,     "Risk_BMV_pre"       ,        "Risk_ASA_pre" ,    "Risk_BMI_pre"         ,      "Risk_cardiorespiratory_pre"),
identify=c("Identify_hypoventilation_pre", "Identify_resprate_pre"     ,   "Identify_allergic_pre"     ,   "Identify_sedationlevel_pre" ,"Respond_hypoventilation_pre", "Respond_hypoxia_pre","Respond_bradycardia_pre", "Respond_hypotension_pre" ),
tech=c("Intervention_OPA_pre"     ,                "Intervention_NPA_pre"          ,           "Intervention_jawsupport_pre"  , 
"Intervention_chinlift_pre" ),
nontech=c("Nontech_access_assistance_pre", "Nontech_respond_pre", "Nontech_assessment_pre"),
total=c("Risk_OSA_pre" ,          "Risk_intubate_pre"     ,     "Risk_BMV_pre"       ,        "Risk_ASA_pre" ,"Risk_comorbidities_pre" ,    "Risk_BMI_pre"         ,      "Risk_cardiorespiratory_pre","Identify_hypoventilation_pre", "Identify_resprate_pre"     ,   "Identify_allergic_pre"     ,   "Identify_sedationlevel_pre" ,"Respond_hypoventilation_pre", "Respond_hypoxia_pre","Respond_bradycardia_pre", "Respond_hypotension_pre","Intervention_OPA_pre"     ,                "Intervention_NPA_pre"          ,           "Intervention_jawsupport_pre"  , 
"Intervention_chinlift_pre" ,"Nontech_access_assistance_pre", "Nontech_respond_pre", "Nontech_assessment_pre"))

post.keys=list(risk=c("Risk_anaesthesia_post","Risk_OSA_post" ,          "Risk_intubate_post"     ,     "Risk_BMV_post"       ,        "Risk_ASA_post" ,    "Risk_BMI_post"         ,      "Risk_cardiorespiratory_post"),
identify=c("Identify_hypoventilation_post", "Identify_resprate_post"     ,   "Identify_allergic_post"     ,   "Identify_sedationlevel_post" ,"Respond_hypoventilation_post", "Respond_hypoxia_post","Respond_bradycardia_post", "Respond_hypotension_post" ),
tech=c("Intervention_OPA_post"     ,                "Intervention_NPA_post"          ,           "Intervention_jawsupport_post"  , 
"Intervention_chinlift_post" ),
nontech=c("Nontech_access_assistance_post", "Nontech_respond_post", "Nontech_assessment_post"),
total=c("Risk_OSA_post" ,          "Risk_intubate_post"     ,     "Risk_BMV_post"       ,        "Risk_ASA_post" ,"Risk_comorbidities_post" ,    "Risk_BMI_post"         ,      "Risk_cardiorespiratory_post","Identify_hypoventilation_post", "Identify_resprate_post"     ,   "Identify_allergic_post"     ,   "Identify_sedationlevel_post" ,"Respond_hypoventilation_post", "Respond_hypoxia_post","Respond_bradycardia_post", "Respond_hypotension_post","Intervention_OPA_post"     ,                "Intervention_NPA_post"          ,           "Intervention_jawsupport_post"  , 
"Intervention_chinlift_post" ,"Nontech_access_assistance_post", "Nontech_respond_post", "Nontech_assessment_post"))
```

```{r}
pre.scales=scoreItems(pre.keys, responsiveness)
pre.scores=pre.scales$scores
post.scales=scoreItems(post.keys, responsiveness)
post.scores=post.scales$scores
```

*Add scale scores to data frame*

```{r}
responsiveness$pre.risk=pre.scores[,1]
responsiveness$pre.identify=pre.scores[,2]
responsiveness$pre.nontech=pre.scores[,3]
responsiveness$pre.tech=pre.scores[,4]
responsiveness$pre.total=pre.scores[,5]

responsiveness$post.risk=post.scores[,1]
responsiveness$post.identify=post.scores[,2]
responsiveness$post.nontech=post.scores[,3]
responsiveness$post.tech=post.scores[,4]
responsiveness$post.total=post.scores[,5]
```

###Describe scale scores

```{r}
plyr::count(responsiveness$pre.tech)
plyr::count(responsiveness$pre.nontech)
plyr::count(responsiveness$pre.risk)
plyr::count(responsiveness$pre.identify)
plyr::count(responsiveness$pre.total)
plyr::count(responsiveness$PSAconfidence_pre)

plyr::count(responsiveness$post.tech)
plyr::count(responsiveness$post.nontech)
plyr::count(responsiveness$post.risk)
plyr::count(responsiveness$post.identify)
plyr::count(responsiveness$post.total)
plyr::count(responsiveness$PSAconfidence_post)
responsiveness$totalchange=responsiveness$post.total- responsiveness$pre.total
responsiveness$Confidence_change=responsiveness$PSAconfidence_post - responsiveness$PSAconfidence_pre
describe(responsiveness[,73:83])
```

```{r}
library(psychometric)

sd=sd(responsiveness$totalchange, na.rm=TRUE)
meanchange=mean(responsiveness$totalchange, na.rm=TRUE)
SRM=meanchange/sd
SRM
GRI=meanchange/sd(responsiveness$pre.total, na.rm=TRUE)
GRI
```

###Plots for paired data

```{r}
new=na.omit(data.frame(responsiveness$pre.total,responsiveness$post.total))
columns2=c("before", "after")
colnames(new)=columns2
totalafter=new$after
totalbefore=new$before

risk=na.omit(data.frame(responsiveness$pre.risk,responsiveness$post.risk))
columns2=c("before", "after")
colnames(risk)=columns2
riskafter=risk$after
riskbefore=risk$before

tech=na.omit(data.frame(responsiveness$pre.tech,responsiveness$post.tech))
columns2=c("before", "after")
colnames(tech)=columns2
techafter=tech$after
techbefore=tech$before

library(PairedData)
total <- paired(totalbefore, totalafter)
plot(total, type = "profile") + theme_bw() +ggtitle("NC-MSCS scores before and after training in sedation") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

risk <- paired(riskbefore, riskafter)
plot(risk, type = "profile") + theme_bw() +ggtitle("Risk subscale scores before and after training in sedation") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

tech <- paired(techbefore, techafter)
plot(tech, type = "profile") + theme_bw() +ggtitle("Technical skills subscale scores before and after training in sedation") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

```

2. Risk

```{r}

```

Plot of correlations

```{r}
ggplotRegression(lm(totalchange ~ Confidence_change, data = responsiveness))

```

### 2020-08-08 manuscript.rmd
targets and draft manuscript complete

---
title: "Development and validation of the nursing confidence in managing sedation complications scale"
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      phone: +1 416 946 7112
      address: 585 University Ave | Toronto, ON  M5G 2N2
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Kristina Chang MScN:
      institute: [PMCC]
      correspondence: false
  - Navpreet Kamboj BScN:
      institute: [LBFON]
      correspondence: false
  - Shahvand Masihi:
      institute: [IR]
      correspondence: false
  - Sebastian Mafeld:
      institute: [IR]
      correspondence: false
  - Joanna Sutherland MBBS:
      institute: [NSW, Coffs]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
  - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
  - NSW: Rural Clinical School, University of New South Wales, Coffs Harbour, NSW, Australia
  - Coffs: Department of Anaesthesia, Coffs Harbour Health Campus, Coffs Harbour, NSW, Australia
  - IR: Interventional Radiology, JDMI, Toronto General Hospital
bibliography: Extras/references.bib
csl: Extras/harvard.csl
output:
  officedown::rdocx_document:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
editor_options:
  markdown:
    canonical: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

library(targets)
library(magrittr)
library(flextable)
library(officedown)

```

\pagebreak

## Abstract

### Introduction

### Methods

### Results

### Conclusion

Keywords: deep sedation, conscious sedation, patient safety, self-efficacy, nursing, scale development, item response theory

\pagebreak

## Declarations

Availability of data and material (data transparency): All data used is available [here](https://github.com/awconway/nc-mscs).

Code availability: Code to reproduce the analyses is available [here](https://github.com/awconway/nc-mscs) and is archived [here]().

Abbreviated title: Nursing confidence in managing sedation complications scale

Funding statement: Support was provided solely from institutional and/or departmental sources.

Conflicts of interest: The authors declare no competing interests.

Author contributions: AC: Study design, data analysis and wrote manuscript; KC: Revised the manuscript for important intellectual content; NK: Revised the manuscript for important intellectual content; JS: Study design, data collection, revised the manuscript for important intellectual content.

\pagebreak

## Introduction

Sedative and analgesic medications can be administered to manage pain, discomfort and anxiety or distress during medical procedures that do not require general anaesthesia. This practice is referred to as procedural sedation and analgesia (PSA) [@apfelbaum2018practice]. It is common for nurses to administer the sedative and analgesic medications according to prescription from the medical practitioner performing the procedure and to monitor the patient (termed nurse-administered PSA) [@Conway_2014]. However, complications are known to arise during PSA due to side effects of sedative and analgesic medications [@apfelbaum2018practice]. For example, the sedative medications typically used can cause the passage of air into the lungs to become partially obstructed. The analgesic medications used (typically the opioids) can also cause the breathing rate to become irregular. If such complications are not detected and corrective interventions applied, the level of oxygen circulating in the blood can drop to a level that is insufficient for the body's requirements (a condition known as hypoxaemia). If severe enough and left uncorrected, hypoxaemia can result in permanent damage to vital organs, such as the brain and heart, potentially causing serious adverse evnts, such as permanent neurological disability or death. Intervening at or soon after the onset of complications can prevent these adverse events from occurring. Therefore, prompt detection and treatment of sedation-related complications is vital to ensure patient safety during procedures performed with PSA [@Bhananker_2006].

Self-efficacy is a measure of one's beliefs in their capability to produce given attainments [@Bandura_1995]. Previous research has demonstrated that people will exert maximal effort and persist despite failure if they believe they are capable in completing a given task [@bandura1999self]. In the healthcare context, it has been shown that clinicians who lack confidence in their abilities do not take needed actions for their patients [@Johnson_2001]. Therefore, it is possible that nurses may not take actions to manage sedation-related complications if they lack confidence in their abilities to complete the necessary tasks. Despite clear relevance, there has been no research about nurses' self-efficacy in managing the complications that arise due to side effects of sedation and analgesic medications administered during medical procedures. For this reason, the aim of this study is to develop an instrument that measures nurses' self-efficacy in managing complications that are known to arise due to side effects of sedative and analgesic medications administered during medical procedures. We have named this instrument the Nursing Confidence in Managing Sedation Complications Scale (NC-MSCS). Once validated, the NC-MSCS could be used in practice to inform the development and evaluation of nursing education programs about the management of complications during sedation. The scale could also be used in the research context as an instrument to compare the effectiveness of different nursing education programs about procedural sedation in improving nursing confidence. Self-efficacy is an individual's perception of their ability to be successful in a given endeavour people tend to undertake behaviors within their range of self-efficacy and avoid those they perceive would exceed their ability.

## Methods

The NC-MSCS was developed and validated through three phases. Content validity of the items was evaluated in the first phase with input from an expert panel of clinicians with expertise in procedural sedation. In the second phase, a survey study was undertaken for item reduction and to evaluate the structural validity of the scale. In the third phase, responsiveness was evaluated using a pre-test post-test design.

### Participants

#### Expert panel

Clinicians who were known to the authors as having expertise in the area of nurse-administered sedation were invited to participate. These included senior clinicians who have developed education programs or competency assessments for the administration of procedural sedation and analgesia or researchers who have published on the topic.

#### Online survey

Inclusion criteria for this phase of the study were nurses who administer, or monitors patients who have received, procedural sedation and analgesia during a medical procedure. An invitation to participate with a link to an online survey was distributed through Interventional Nursing Council of the Cardiac Society of Australia and New Zealand, Australian College of Operating Room Nurses, Medical Imaging Nurses Association, Gastroenterological Nurses College of Australia, Thoracic Society of Australia and New Zealand Respiratory Nurses Special Interest Group and the College of Emergency Nursing Australia.

#### Pre-test post-test study

Nurses who were undergoing a one-day procedural sedation education session delivered by one of the authors (JS) were invited to participate.

### Measurement tools

#### Expert panel

An initial bank of items for potential inclusion in the NC-MSCS was created. Items were chosen based on the authors' clinical experience as well as from clinical practice guidelines for procedural sedation [@apfelbaum2018practice; @Conway_2014; @conway2013; @conway2013a; @sutherland2020]. Each item was prefixed with the phrase, 'I am confident I am able to...\". Responses were measured on a 7-point scale, ranging from 'strongly disagree' to 'strongly agree'.

The initial bank of items for the NC-MSCS were assessed for relevance using a 4-point scale (1=not relevant; 2=somewhat relevant; 3=quite relevant; 4=highly relevant). In addition, there was free-text space for the expert panel participants to provide suggestions to increase clarity of the wording of the items and to suggest additional items. The draft bank of items comprised four conceptual domains with a total of 37 items. Domain one included 6 items that measure nurses' confidence in identifying patients who are at greater risk of a sedation-related complication based on a pre-procedural assessment. Domain two included 14 items that measure nurses' confidence in identifying and responding to sedation-related complications. Domain three included 11 items that measure nurses' confidence in identify the situations in which different interventions to treat sedation-related complications may be required. Domain four included 7 items that measures nurses' confidence in the technical skills required for interventions to treat sedation-related complications.

#### Online survey

*NC-MSCS:* The items identified by the expert panel as being relevant to the measurement of nursing confidence in managing the complications of sedation were included in the survey. They were presented to respondents participating in the online survey in a random order.

*Sedation experience and education:* Nurses were asked a series of questions in order to ascertain the extent of the experience and education in aspects related to the management of sedation-related complications.

*General Self-efficacy:* The New General Self-efficacy scale (NGSE) was also included in the online survey [@chen2001]. It consists of 8 items that has demonstrated high reliability, discriminant validity and predictive validity [@chen2001]. The NGSE scale is scored on a 5-point scale from strongly disagree (1) to strongly agree (5).

#### Pre-test post-test study

Time was allocated at the start and end of the education session to allow those nurses who chose to take part in the study to complete the NC-MSCS. In addition to the NC-MSCS, participants responded to a set of items designed to ascertain the extent of their experience and education in aspects related to the management of sedation-related complications. Participants were also asked to rate the extent to which their overall knowledge and confidence changed from before to after the sedation training, using a 7-point rating scale from (1) greatly decreased to (7) greatly increased.

### Statistical considerations and data analysis

#### Sample size considerations

We aimed to recruit 8-10 participants for the expert panel survey, as has been recommended for content validation.[@Polit_2007] We aimed to recruit 200 participants for the nurse survey. A sample of this size met a recommended minimum necessary sample size for factor analysis (assuming the variables-to-factors ratio was not lower than 5) [@Mundfrom_2005]. For the pre-test post-test phase of the study, the total number of participants was limited by the number of nurses participating in the education sessions. Therefore, no specific power analysis was performed in order to calculate the sample size.

#### Statistical methods

For the expert panel survey, ratings of the relevance of items were used to compute the content validity index for each item by averaging the proportion of respondents that rated the item as a 3 or 4 (i.e. 'quite relevant' or 'highly relevant')[@Polit_2007]. Items with a content validity index of less than 0.78 were considered for revision and those with very low index values were considered for deletion[@Polit_2007]. In addition, the research team revised the wording of items based on panel members' responses regarding the clarity of items.

For item reduction and examination of the structural validation of the NC-MSCS, the following analyses were undertaken using nurses' responses from the online survey. Ordinary least squares estimations with a matrix of polychoric correlations was generated for an exploratory factor analysis due to the use of ordinal response variables [@Gaskin_2014]. Parallel analysis was used to determine the optimal number of factors for extraction and principal axis factoring with promax rotation was used for factor extraction. Internal consistency, calculated using Cronbach's alpha coefficient, was calculated to examine the reliability of the scale. There was less than 2% missing data for all scale items. We imputed missing values using expectation maximization [@fox-wasylyshyn2005].

Construct validity was evaluated by using multivariable linear regression to identify associations between scores on the NC-MSCS and nurses' experience and education regarding sedation. We hypothesised that higher scores on the NC-MSCS would be associated with:

-   nurses who reported more years of experience administering sedation
-   nurses who reported more years of experience in nursing
-   nurses who worked in departments that provided formal education in sedation
-   nurses who were certified in ALS
-   nurses who administered sedation more frequently
-   nurses who have higher ratings for general self-efficacy (measured using the NGSE) [@chen2001]
-   nurses who rated their knowledge about sedation higher
-   nurses who worked in critical care (emergency department/ICU/PACU) or anaesthesia.

To evaluate responsiveness, analyses focused on testing the hypothesis that there would be a positive correlation between the change in participants NC-MSCS scores and changes in participant ratings of their overall knowledge and confidence in managing sedation complications from before to after undertaking a training course in sedation. Linear regression was used to determine the association between total NC-MSCS scores with participants' ratings of overall knowledge and confidence in managing PSA complications as well as change in knowledge and confidence from pre to post training in sedation and general self-efficacy scale scores. We used Tufte Slopegraph to visually display the change in NC-MSCS scores from the pre to post time-points, and used bootstrap estimation (5000 resamples) to calculate the mean difference with 95% confidence intervals [@ho2019]. A standardized response mean (mean change divided by the standard deviation of the change score) was also calculated.

## Results

### Content validity

We received responses from nine participants for the expert panel. Pre-specified criteria for content validity was met with the item-content validity index being higher than 0.78 for 34 items and the scale content validity index was 0.91.

### Structural validity

Usable data for the analyses was obtained from `r nrow(targets::tar_read(ncmscs_items))` nurses. Demographic characteristics are presented in Table \@ref(tab:tab1). The majority of the sample was highly experienced both in terms of total years in nursing and the number of years experience with procedural sedation.

Before the main analysis, the appropriateness of factor analysis was considered. The Kaiser-Meyer-Olkin measure of sampling adequacy was high at `r round(targets::tar_read(factorability)$MSA, 2)`. Examination of the scree plot (Figure \@ref(fig:scree)) and parallel analysis indicated that a 3-factor solution was appropriate. Items that did not meet criteria were deleted one at a time with factor analyis repeated after each item deletion. We repeated this process until all items retained had a factor loading of at least 0.40 and loaded on one coherent factor. The original scale was reduced from 34 to 18 items (Figure \@ref(fig:facanalysis)). Eight items were removed because there were high loadings (\>.35) on more than one subscale, with loading differences \<.15. A further eight items were removed because the items did not load on a conceptually consistent subscale. For example, the item "I am confident I am able to identify laryngospasm", loaded with items related to risk assessment. Subscales were named 1) Risk assessment; 2) Identifying and responding to cardiorespiratory complications; 3) Technical airway skills. The subscales together accounted for 65.6% of the variance in the scale. Cronbach's alpha for the 18-item scale (Cronbach's 𝛂 `r round(targets::tar_read(reliability_total)$total$std.alpha, 2)`) and each subscale was high (Cronbach's 𝛂 \>0.85). The minimum score for the 18-item NC-MSCS is 18 and maximum is 126. The distribution of scores is presented in Figure \@ref(fig:dist). The technical airway skills and identifying and responding to cardiorespiratory complications subscales were heavily right-skewed.

### Construct validity

Construct validity was established with significant differences (p\<0.001) in NC-MSCS scores relative to years of nursing experience and specialty area of practice (critical care/anaesthesia nurses reported higher NC-MSCS scores than procedural/operating theatre nurses) (Table \@ref(tab:construct)). Statistically significant positive correlations between NC-MSCS scores and participant ratings of knowledge and confidence in managing procedural sedation as well as perceived general self-efficacy were also observed (Figure 1).

### Responsiveness

A total of `r nrow(targets::tar_read(resp_change))` participated in the pre-test post-test study. Characteristics for participants included in this phase of the study are displayed in Table \@ref(tab:resptable). On average, participants had approximately 4 years of experience administering sedation but reported only infrequently being required to administer or monitor patients who have received procedural sedation in a typical working week. Score distributions for each subscale and the total scale for the pre-test are presented in Figure \@ref(fig:predist). The change in NC-MSCS scores, displayed in Figure \@ref(fig:change), increased significantly from pre to post-training in sedation (mean difference = `r glue::glue("{round(targets::tar_read(paired_diff)$result$difference, 1)}; 95% CI = {round(targets::tar_read(paired_diff)$result$pct_ci_low, 1)} to {round(targets::tar_read(paired_diff)$result$pct_ci_high, 1)}")`). In addition, the change in NC-MSCS scores were positively correlated with the change in participants' ratings of overall confidence and knowledge about management of PSA complications (Figure \@ref(fig:reg)). The standardized response mean, adjusted for the correlation between pre and post measurements, was `r targets::tar_read(change_summaries)$SRMadj`.

## Discussion

The aim of this study was to develop a scale to measure nursing confidence in managing sedation-related complications. A large sample of nurses with diverse clinical experience across the numerous specialties in which sedation is frequently used participated in the study. This provided the opportunity to eliminate redundancy from an inital comprehensive item pool, which was created by the authors of this study but refined by an expert panel using a rigorous process for establishing content validity [@Polit_2007]. The resultant 18-item NC-MSCS demonstrated a robust 3-factor structure with high internal consistency overall, as well as for each subscale measuring the domains of confidence in risk assessment, identification and responses to cardiorespiratory complications and application of airway interventions. Importantly, the scale was able to distinguish between-group differences based on specialty expertise. Nurses who worked in critical care areas (defined as ICU, emergency or anaesthesia/recovery) reported considerably higher levels of confidence in managing sedation-related complications compared with nurses who worked in other specialties (eg. cardiac cath lab, radiology, endoscopy surgery). Effect sizes for associations between NC-MSCS and years of experience in nursing, general self-efficacy and general knowledge about managing sedation-related complications were statistically significant but very small.

The NC-MSCS does not attempt to measure overcomplicated activities or tasks that go beyond nurses' knowledge or competences related to administering and monitoring procedural sedation, which have been outlined in clinical practice guideline statements from professional societies [@apfelbaum2018practice; @conway2013]. The 18-item NC-MSCS offers a very quick and simple tool for measuring self-efficacy in performing such aspects of procedural sedation management. Although no prior research has specifically examined the effect of low levels on confidence toward the optimal management of sedation-related complications, research from other similar clinical contexts provides some insight. For example, research in the resuscitation context has consistently demonstrated that lack of confidence is a barrier to achieving good quality cardiopulmonary resuscitation [@vaillancourt2013; @roh2012]. Therefore, the NC-MSCS could be a useful tool for self-reflection, or to guide and inform sedation training initiatives and to inform formal competency assessment activities. An online version of the complete scale can be accessed and scored [here](https://nc-mscs.netlify.app/).

The right-skewed distribution of subscale scores in the online survey should be noted. We used polychoric correlations for the exploratory factor analysis, which is the recommended approach for skewed data [@Gaskin_2014; @vandereijk2015]. Although the potential for a ceiling effect should not be ruled out, it is reassuring that the distribution of scores in the pre-sedation training group was not right-skewed. It is likely the higher ratings for items within these particular subscales that were observed in the online survey were associated with specific characteristics of the sample, such as participants' years of experience in nursing and the clinical settings in which the participants practiced (e.g. critical care setting versus procedural/medical settings).

<!--# The factor structure identified through exploratory factor analysis did not exactly align with the conceptual framework we used to create the initial bank of items. The bank of items was constructed with a tentative 4-domain structure, whereas parallel analysis indicated a 3-factor structure was the most parsimonious solution.  -->

The sample for the online survey was highly experienced and reported high levels of confidence in managing sedation complications. A convenience sampling approach and recruitment of participants through professional nursing organizations is the likely reason for. The sample is therefore not entirely representative of the broader population of nurses who are involved in the management of procedural sedation. Prior research has identified that although sampling through professional organizations is a convenient approach to access a more broadly geographically distributed sample, it does not adequately represent the characteristics of the population [@gillespie2010sampling]. Conducting confirmatory factor analysis with a different sample of nurses would be useful to determine if the factor structure we identified is robust to sampling procedures.

<!--# The risk assessment and identification/responses to cardiorespiratory complications factors explained a considerably percentage of variance than the factor containing items related to technical airway skills. Different patient characteristics in the responsiveness study. -->

If adjusted for the correlation between pre and post measurements, Cohen's rule-of-thumb thresholds for interpreting effect size can be applied for the standardized response mean, which was one statistic we used to assess responsiveness of the NC-MSCS [@sivan2009; @cohen2013statistical]. Results indicate there was a large improvement in confidence in the pre-test post-test study (SRMadj 1.3). In addition, there was a positive and strong relationship between changes in the NC-MSCS from pre to post training with perceived changes in overall knowledge and confidence. It is reassuring that the NC-MSCS was able to detect a change in participants' confidence after undertaking a formal education session in management of sedation. Undertaking further investigations, such as test-retest reliability to determine the minimal detectable difference in NC-MSCS scores, would be required in order for this scale to be used with confidence as a measure to judge the effectiveness of particular sedation training programs/modes of sedation training. For example, considering the not insignificant costs associated with in-person training, there may be advantages to delivering all or part of sedation education using more affordable and accessible online virtual modalities [@tobin2013]. One way the efficacy of these alternative approaches could be compared would be to use the NC-MSCS as an outcome measure.

In many institutions, considerable time and effort is directed towards annual compentency assessments for a variety of aspects of clinical care. Competency in procedural sedation is one such area. The timeframe for such assessments, however, seems to be arbitrarily set and there is limited consideration of tailoring assessment to nurses individual capabilitlies and education needs. Application of the NC-MSCS in education practice could be useful as a tool to stratify more experienced nurses to receive either further education and training in sedation (low confidence) or straight to simulation testing to ensure inaccurate calibration (high confidence but poor performance) is not an issue.

### Limitations

Respondents in the online survey were relatively homogenous in regard to having a large amount of experience in sedation as well as being highly experienced nurses. We recommend future testing of the NC-MSCS in samples with greater heterogeneity. The use of a professional organisations gives rise to selection bias. A convenience sampling approach was used for the pre-test post-test study. As such, selection bias may have influenced the results of the analyses conducted to evaluate the responsiveness of the NC-MSCS. Further psychometric testing to establish criterion-related validity and test--retest reliability would strengthen confidence in the usefullness of the NC-MSCS.

### Conclusion

Self-efficacy is a strong predictor of the level of accomplishment that individuals attain [@bandura1999self]. Nurses may fail to apply their knowledge and skills successfully unless they have an adequate level of self-efficacy in tasks related to management of procedural sedation. The psychometric properties of the NC-MSCS appear encouraging. Further testing of the instrument is required in different samples to provide further evidence of validity and to determine the minimal important difference. A particularly important further test of the validity of the NC-MSCS will be to determine if higher levels of confidence (as assessed by the scale) are associated with safer patient care. This scale could be used to guide and inform education and training of nurses as well as complement formal competency assessment.

\pagebreak

## References

::: {#refs}
:::

\pagebreak

## Figure legend

Fig. \@ref(fig:scree) Scree plot from initial factor analysis of the Nursing-Confidence in Managing Sedation Complications Scale

Fig. \@ref(fig:facanalysis) Rotated factor loadings for the Nursing Confidence in Managing Sedation Complications Scale

Fig. \@ref(fig:dist) Distribution of Nursing Confidence in Managing Sedation Complications Scale and subscale scores in the online survey

Fig. \@ref(fig:predist) Pre-sedation training distribution of Nursing Confidence in Managing Sedation Complications Scale and subscale scores

Fig. \@ref(fig:change) Change in Nursing Confidence in Managing Sedation Complications Scale scores from pre to post-training

Fig. \@ref(fig:reg) Association between change in Managing Sedation Complications Scale scores from pre to post-training with (A) change in overall rating of confidence in managing sedation; and (B) change in overall knowledge about sedation.

\pagebreak

```{r tab.cap='Participant characteristics for online survey', tab.id = 'tab1'}
targets::tar_load(characteristics_table)
gtsummary::as_flextable(characteristics_table) %>%
  flextable::width(j= "label",width = 4) %>%
  flextable::width(j= "stat_0",width = 1)

```

\pagebreak

```{r tab.cap='Multivariable regression model of associations between NC-MSCS score and participant characteristics', tab.id='construct'}
targets::tar_read(overall_model)  %>% 
  dplyr::mutate(term = dplyr::case_when(term == "YearsNursing" ~ "Years in nursing",
term == "YearsPSA" ~ "Years of experience administering sedation",
term == "PSAFrequency" ~ "Frequency of administering sedation in a typical working week",
term =="ALS" ~ "Trained in Advanced Life Support",
term == "PSAEducation" ~ "Received education about sedation",
term == "GSE" ~ "New General Self-efficacy Score",
term == "critcareTRUE" ~ "Works in a critical care environment",
term == "OverallKnowledge" ~ "Perceived knowledge about managing sedation-related complications",
TRUE ~ as.character(term))) %>%
                dplyr::select(Variable = term,
                  `𝛃` = estimate,
                              -`std.error`,
                              `p-value` = p.value,
                              `Lower 95% CI` = conf.low,
                              `Upper 95% CI` = conf.high)%>% 
           flextable::flextable() %>% 
  flextable::colformat_num(digits = 3) %>%
  flextable::width(j=1,width = 3)

```

\pagebreak

```{r tab.cap="Participant characteristics for pre-test post-test study", tab.id = 'resptable'}
targets::tar_load(resp_char_table)
  gtsummary::as_flextable(resp_char_table) %>%
  flextable::width(j= "label",width = 4) %>%
  flextable::width(j= "stat_0",width = 1)
```

<!---BLOCK_MULTICOL_START--->

<!---BLOCK_STOP--->

<!--BLOCK_LANDSCAPE_START--->

```{r scree, fig.cap = "Scree plot from initial factor analysis of the Nursing-Confidence in Managing Sedation Complications Scale", fig.width=9}
targets::tar_read(screePlot)
```

\pagebreak

```{r facanalysis, fig.cap = "Rotated factor loadings for the Nursing Confidence in Managing Sedation Complications Scale", fig.width=9}
targets::tar_read(ncmscs_plot)
```

\pagebreak

```{r dist, fig.cap = "Distribution of Nursing Confidence in Managing Sedation Complications Scale and subscale scores in the online survey", fig.height=5.5, fig.width=9}
targets::tar_read(comb_dist_plot)
```

\pagebreak

```{r predist, fig.cap = "Pre-sedation training distribution of Nursing Confidence in Managing Sedation Complications Scale and subscale scores", fig.height=5.5, fig.width=9}
targets::tar_read(pre_comb_dist_plot)
```

\pagebreak

```{r change, fig.cap = "Change in Nursing Confidence in Managing Sedation Complications Scale scores from pre to post-training"}

targets::tar_read(paired_plot)

```

<!---BLOCK_LANDSCAPE_STOP--->

```{r reg, fig.cap="Association between change in Managing Sedation Complications Scale scores from pre to post-training with (A) change in overall rating of confidence in managing sedation; and (B) change in overall knowledge about sedation", fig.height=7}

targets::tar_read(comb_reg)

```

### 2020-08-08 R/add_modelling_vars.R

@@ -1,0 +1,17 @@
+#' Add variables for models
+#' @export
+#' @importFrom dplyr rowwise mutate c_across ungroup
+#'
+add_modelling_vars <- function(data) {
+  data$critcare <- data$Specialty == 10 | data$Specialty == 9 | data$Specialty == 8 | data$Specialty == 7
+
+
+  rf <- rowwise(data)
+
+  rf <- rf %>%
+    mutate(GSE = sum(c_across(contains("GSES"))))
+
+
+
+  ungroup(rf)
+}

### 2020-08-08 R/add_totals.R

@@ -1,0 +1,15 @@
+
+#' Add subscale scores
+#' @export
+#' @importFrom psych scoreItems
+#'
+add_totals <- function(data, keys) {
+  my.scales.3 <- scoreItems(keys, data, totals = TRUE)
+  my.scores.3 <- my.scales.3$scores
+  # Add scale scores to data frame
+  data$risk <- my.scores.3[, 1]
+  data$cardioresp <- my.scores.3[, 2]
+  data$airway <- my.scores.3[, 3]
+  data$ncmscs_total <- my.scores.3[, 4]
+  return(data)
+}

### 2020-08-08 R/factor.R

@@ -1,0 +1,10 @@
+#' @title Factor analysis
+#' @rdname factor
+#' @export
+#' @importFrom psych polychoric fa
+
+
+factor <- function(ncmscs_factor_df) {
+  polycor <- polychoric(ncmscs_factor_df, smooth = FALSE)
+  fa(polycor$rho, nfactors = 3, rotate = "Promax", fm = "ols")
+}

### 2020-08-08 R/factor_plot.R

@@ -1,0 +1,47 @@
+#' Plot of loadings
+#' @export
+#' @importFrom ggplot2 ggplot aes facet_wrap geom_bar
+#' coord_flip scale_fill_gradient2 ylab theme_bw
+#' @importFrom plyr mapvalues
+
+factor_plot <- function(data) {
+  t <- as.table(print(data$loadings))
+  t1 <- as.data.frame(t)
+  t1$Var2 <- mapvalues(t1$Var2, from = c("A", "B", "C"), to = c("Identify and respond", "Risk assessment", "Technical skills"))
+  t1$Var1 <- mapvalues(t1$Var1, from = c(
+    "RiskHistory", "RiskOSA", "DifficultIntubate", "DifficultBMV",
+    "RiskASA", "RiskBMI", "RiskCardioresp",
+    "IdentifyRespRate",
+    "IdentifyBradycardia", "IdentifyHypotension", "RespondHypoventilation",
+    "RespondHypoxia", "RespondBradycardia", "RespondHypotension",
+    "OPA", "NPA", "JawSupport",
+    "ChinLift"
+  ), to = c(
+    "Assess risk from anaesthetic history", "Assess risk from sleep apnoea", "Determine risk for difficult intubation", "Determine risk for difficult bag mask ventilation",
+    "Assess risk from ASA classification status", "Assess risk from body mass index", "Assess risk from cardiorespiratory reserve",
+    "Identify abnormal respiratory rate",
+    "Identify bradycardia", "Identify hypotension", "Respond to hypoventilation",
+    "Respond to hypoxia", "Respond to bradycardia", "Respond to hypotension",
+    "Insert oropharyngeal airway", "Insert nasopharyngeal airway", "Apply jaw support",
+    "Apply chin lift"
+  ))
+  names <- c("Item", "Factor", "Loading")
+  colnames(t1) <- names
+
+  # For each test, plot the loading as length and fill color of a bar
+  # note that the length will be the absolute value of the loading but the
+  # fill color will be the signed value, more on this below
+
+  ggplot(t1, aes(Item, abs(Loading), fill = Loading)) +
+    facet_wrap(~Factor, nrow = 1) + # place the factors in separate facets
+    geom_bar(stat = "identity") + # make the bars
+    coord_flip() + # flip the axes so the test names can be horizontal
+    # define the fill color gradient: blue=positive, red=negative
+    scale_fill_gradient2(
+      name = "Loading",
[…]

### 2020-08-08 R/ggplotRegression.R

@@ -1,0 +1,74 @@
+#' Knowledge regression plot
+#' @name ggplotRegression_know
+#' @export
+#' @importFrom ggplot2 ggplot aes stat_smooth labs theme_bw theme
+#' element_blank element_line aes_string
+ggplotRegression_know <- function(fit) {
+  ggplot(fit$model, aes_string(
+    x = names(fit$model)[2],
+    y = names(fit$model)[1]
+  )) +
+    geom_point() +
+    theme_bw() +
+    theme(
+      panel.border = element_blank(),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      axis.line = element_line(colour = "black")
+    ) +
+    stat_smooth(method = "lm", col = "red") +
+    labs(
+      caption = paste(
+        "Adj R squared = ", signif(summary(fit)$adj.r.squared, 3),
+        "Intercept =", signif(fit$coef[[1]], 3),
+        " Slope =", signif(fit$coef[[2]], 3),
+        " P =", format(summary(fit)$coef[2, 4], scientific = F, digits = 3)
+      ),
+      y = "Post minus pre NC-MSCS",
+      x = "Post minus pre perceived overall knowledge about sedation"
+    )
+}
+
+#' Confidence regression plot
+#' @name ggplotRegression_conf
+#' @export
+#' @importFrom ggplot2 ggplot aes stat_smooth labs theme_bw theme
+#' element_blank element_line aes_string
+ggplotRegression_conf <- function(fit) {
+  ggplot(fit$model, aes_string(
+    x = names(fit$model)[2],
+    y = names(fit$model)[1]
+  )) +
+    geom_point() +
+    theme_bw() +
+    theme(
+      panel.border = element_blank(),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      axis.line = element_line(colour = "black")
+    ) +
+    stat_smooth(method = "lm", col = "red") +
+    labs(
+      caption = paste(
+        "Adj R squared = ", signif(summary(fit)$adj.r.squared, 3),
+        "Intercept =", signif(fit$coef[[1]], 3),
+        " Slope =", signif(fit$coef[[2]], 3),
+        " P =", format(summary(fit)$coef[2, 4], scientific = F, digits = 3)
+      ),
+      y = "Post minus pre NC-MSCS",
+      x = "Post minus pre perceived overall confidence managing sedation"
+    )
+}
+
[…]

### 2020-08-08 R/impute_missing.R

@@ -1,0 +1,8 @@
+#' @title Impute missing data
+#' @importFrom TestDataImputation EMimpute
+#' @export
+#'
+impute_missing <- function(data) {
+  data <- as.matrix(data)
+  EMimpute(data, Mvalue = "NA", max.score = 7)
+}

### 2020-08-08 R/keys_responsive.R

@@ -1,0 +1,90 @@
+#' Add scale scores
+#' @export
+#' @importFrom psych scoreItems
+#'
+keys_responsive <- function(responsiveness) {
+  pre.keys <- list(
+    risk = c(
+      "Risk_anaesthesia_pre", "Risk_OSA_pre", "Risk_intubate_pre",
+      "Risk_BMV_pre", "Risk_ASA_pre", "Risk_BMI_pre",
+      "Risk_cardiorespiratory_pre"
+    ),
+    airway = c(
+      "Intervention_OPA_pre", "Intervention_NPA_pre", "Intervention_jawsupport_pre",
+      "Intervention_chinlift_pre"
+    ),
+    cardioresp = c(
+      "Identify_resprate_pre",
+      "Identify_bradycardia_pre",
+      "Identify_hypotension_pre",
+      "Respond_hypoventilation_pre", "Respond_hypoxia_pre",
+      "Respond_bradycardia_pre", "Respond_hypotension_pre"
+    ),
+    total = c(
+      "Risk_anaesthesia_pre", "Risk_OSA_pre", "Risk_intubate_pre",
+      "Risk_BMV_pre", "Risk_ASA_pre", "Risk_BMI_pre",
+      "Risk_cardiorespiratory_pre",
+      "Intervention_OPA_pre", "Intervention_NPA_pre", "Intervention_jawsupport_pre",
+      "Intervention_chinlift_pre",
+      "Identify_resprate_pre",
+      "Identify_bradycardia_pre",
+      "Identify_hypotension_pre",
+      "Respond_hypoventilation_pre", "Respond_hypoxia_pre",
+      "Respond_bradycardia_pre", "Respond_hypotension_pre"
+    )
+  )
+
+  post.keys <- list(
+    risk = c(
+      "Risk_anaesthesia_post", "Risk_OSA_post", "Risk_intubate_post",
+      "Risk_BMV_post", "Risk_ASA_post", "Risk_BMI_post",
+      "Risk_cardiorespiratory_post"
+    ),
+    airway = c(
+      "Intervention_OPA_post", "Intervention_NPA_post", "Intervention_jawsupport_post",
+      "Intervention_chinlift_post"
+    ),
+    cardioresp = c(
+      "Identify_resprate_post",
+      "Identify_bradycardia_post",
+      "Identify_hypotension_post",
+      "Respond_hypoventilation_post", "Respond_hypoxia_post",
[…]

### 2020-08-08 R/ncmscsitems.R

@@ -1,0 +1,7 @@
+#' @title Impute missing data
+#' @importFrom TestDataImputation EMimpute
+#' @export
+#'
+impute <- function(data) {
+  EMimpute(data, Mvalue = "NA", max.score = 7)
+}

### 2020-08-08 R/scree_plot.R

@@ -1,0 +1,31 @@
+#' @title Scree plot
+#' @export
+#' @importFrom nFactors nScree parallel plotnScree
+#' @importFrom psych polychoric
+#' @importFrom tibble rowid_to_column
+#' @importFrom tidyr pivot_longer
+#' @importFrom dplyr select
+#' @importFrom  ggplot2 aes ggplot geom_line geom_point theme element_blank
+#'
+scree_plot <- function(ncmscs_items) {
+  polycor <- polychoric(as.matrix(ncmscs_items), smooth = FALSE)
+  ev <- eigen(cor(polycor$rho))
+  ap <- parallel(
+    subject = nrow(polycor$rho), var = ncol(polycor$rho),
+    rep = 100, cent = .05, model = "factors"
+  )
+  nS <- nScree(x = ev$values, aparallel = ap$eigen$qevpea)
+  pa <- nS$Analysis
+
+  pa %>%
+    rowid_to_column("Components") %>%
+    select(Components,
+      `Parallel Analysis` = `Par.Analysis`,
+      Eigenvalues
+    ) %>%
+    pivot_longer(cols = -Components, names_to = "type", values_to = "Eigenvalues") %>%
+    ggplot(aes(y = Eigenvalues, x = Components, color = type)) +
+    geom_line() +
+    geom_point() +
+    theme(legend.title = element_blank())
+}

### 2020-08-08 R/tar_missing.R

@@ -1,0 +1,7 @@
+#' @title Amount of missing data
+#' @export
+#'
+#'
+tar_missing <- function(ncmscs_full) {
+  (sum(is.na(ncmscs_full)) / prod(dim(ncmscs_full))) * 100
+}

### 2020-08-08 _targets.R

@@ -1,0 +1,279 @@
+library(targets)
+
+devtools::load_all()
+load("data/data.Rdata")
+# Define targets
+tar_pipeline(
+  tar_target(ncmscs_full, data[, 24:57]),
+  tar_target(missing, tar_missing(ncmscs_full)),
+  tar_target(ncmscs_imp, impute_missing(ncmscs_full)),
+  # Sedation reversal – worded with more than one part in the question
+  # Laryngeal mask airway – not all trained for this
+  # AssessLevel Sedation - wording was too similar to identify over-sedation
+  tar_target(ncmscs_items, ncmscs_imp %>%
+    dplyr::select(
+      -Medication,
+      -LMA,
+      -AssessLevelSedation
+    )),
+  tar_target(
+    factorability,
+    psych::KMO(ncmscs_items)
+  ),
+  tar_target(screePlot, scree_plot(ncmscs_items)),
+  # Remove RiskComorbidity, RespondObstruction,
+  # IdentifyHypoventilation, BMV
+  #   because difference <0.15
+  # Remove RiskFrailty because it loaded on the wrong factor
+  # Remove NontechAccessAssist because of Heywood case
+  # This solution identified a factor structure consisting of:
+  # 1. Advanced airway assessment skills
+  # 2. Technical skills related to airway patency
+  # 3. General skills related to identifying and responding to
+  # sedation-related complications.
+  # Removed the non-technical items and additional 'identify' items becuase they
+  # didn't load consistently on one of the conceptually derived factors
+  tar_target(ncmscs_factor_df, ncmscs_items %>%
+    dplyr::select(
+      -RiskComorbid,
+      -IdentifyHypoventilation,
+      -BMV,
+      -RespondObstruction,
+      -RiskFrailty,
+      -NontechAccessAssist,
+      -IdentifyObstruction,
+      -IdentifyLaryngospasm,
+      -IdentifyAllergy,
+      -IdentifyOversedation,
+      -NontechRespond,
+      -NontechIdentifyAssist,
+      -NontechAssess
+    )),
+  tar_target(ncmscs_factor, factor(ncmscs_factor_df)),
+  tar_target(keys_list, keys()),
+
+  tar_target(ncmscs_df, add_totals(data, keys_list)),
+  tar_target(ncmscs_plot, factor_plot(ncmscs_factor)),
[…]

### 2020-09-02 manuscript.rmd
submitted to sage open nursing

@@
       correspondence: false
-  - Shahvand Masihi:
-      institute: [IR]
-      correspondence: false
-  - Sebastian Mafeld:
-      institute: [IR]
-      correspondence: false
   - Joanna Sutherland MBBS:
@@
   - Coffs: Department of Anaesthesia, Coffs Harbour Health Campus, Coffs Harbour, NSW, Australia
-  - IR: Interventional Radiology, JDMI, Toronto General Hospital
 bibliography: Extras/references.bib
@@
 ```{r global_options, include=FALSE}
-knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.retina = 5)
 
@@
 
+It is possible that nurses may not take actions to manage sedation-related complications if they lack confidence in their abilities to complete the necessary tasks.
+The aim of this study was to develop the Nursing Confidence in Managing Sedation Complications Scale (NC-MSCS).
+
 ### Methods
+
+An expert panel rated the relevance of an initial bank of items.
+Items with a content validity index of less than 0.78 were revised or deleted.
+An online survey containing items from the revised scale was distributed to nurses who were members of five different specialty nursing associations in Australia.
+Principal axis factoring and promax rotation was used for factor extraction.
+Multivariable linear regression was used to identify associations between scale scores and nurses' experience and education regarding sedation.
+Internal consistency was calculated to examine reliability.
+Responsiveness was evaluated using a pre-test post-test design with a sample of nurses who completed a sedation education program.
 
@@
 
+Pre-specified criteria for content validity was met for 34 items.
+Responses from 228 nurses who participated in the online survey were analysed.
+An 18-item, 3-factor solution was identified as the most parsimonious solution, with subscales accounting for 65.6% of the variance.
+Cronbach's alpha for the scale (`r round(targets::tar_read(reliability_total)$total$std.alpha, 2)`) and subscales was high (\>0.85).
+There were significant differences (p\<0.001) in NC-MSCS scores relative to years of nursing experience and work environment (critical care/anaesthesia versus procedural/operating theatre).
+The change in NC-MSCS scores reported by the 31 nurses who participated in the pre-test post-test study increased significantly from before to after sedation training (mean difference = `r glue::glue("{round(targets::tar_read(paired_diff)$result$difference, 1)}; 95% CI = {round(targets::tar_read(paired_diff)$result$pct_ci_low, 1)}-{round(targets::tar_read(paired_diff)$result$pct_ci_high, 1)}")`).
+Change in NC-MSCS was correlated with the change in overall confidence and knowledge about managing sedation complications.
+
 ### Conclusion
+
+The NC-MSCS is a valid and reliable instrument, which could be used to guide and inform sedation training programs and competency assessments.
 
@@
 
-Code availability: Code to reproduce the analyses is available [here](https://github.com/awconway/nc-mscs) and is archived [here]().
+Code availability: Code to reproduce the analyses is available [here](https://github.com/awconway/nc-mscs).
 
@@
 
-Sedative and analgesic medications can be administered to manage pain, discomfort and anxiety or distress during medical procedures that do not require general anaesthesia.
+Sedative and analgesic medications can be administered to manage pain, discomfort and anxiety or distress during diagnostic and/or interventional procedures that do not require general anaesthesia.
 This practice is referred to as procedural sedation and analgesia (PSA) [@apfelbaum2018practice].
 It is common for nurses to administer the sedative and analgesic medications according to prescription from the medical practitioner performing the procedure and to monitor the patient (termed nurse-administered PSA) [@Conway_2014].
-However, complications are known to arise during PSA due to side effects of sedative and analgesic medications [@apfelbaum2018practice].
-For example, the sedative medications typically used can cause the passage of air into the lungs to become partially obstructed.
-The analgesic medications used (typically the opioids) can also cause the breathing rate to become irregular.
+Complications are known to arise during PSA due to side effects of sedative and analgesic medications [@apfelbaum2018practice].
+For example, the sedative medications can cause relaxation of muscles and hence loss of ability to maintain a patent airway.
+The analgesic medications used (typically the opioids) can also cause the breathing rate to be depressed.
 If such complications are not detected and corrective interventions applied, the level of oxygen circulating in the blood can drop to a level that is insufficient for the body's requirements (a condition known as hypoxaemia).
@@
 
-Self-efficacy is a measure of one's beliefs in their capability to produce given attainments [@Bandura_1995].
+Self-efficacy is a measure of one's beliefs in their own capability to produce given attainments [@Bandura_1995].
 Previous research has demonstrated that people will exert maximal effort and persist despite failure if they believe they are capable in completing a given task [@bandura1999self].
@@
 The scale could also be used in the research context as an instrument to compare the effectiveness of different nursing education programs about procedural sedation in improving nursing confidence.
-Self-efficacy is an individual's perception of their ability to be successful in a given endeavour people tend to undertake behaviors within their range of self-efficacy and avoid those they perceive would exceed their ability.
 
@@
 
-Inclusion criteria for this phase of the study were nurses who administer, or monitors patients who have received, procedural sedation and analgesia during a medical procedure.
-An invitation to participate with a link to an online survey was distributed through Interventional Nursing Council of the Cardiac Society of Australia and New Zealand, Australian College of Operating Room Nurses, Medical Imaging Nurses Association, Gastroenterological Nurses College of Australia, Thoracic Society of Australia and New Zealand Respiratory Nurses Special Interest Group and the College of Emergency Nursing Australia.
+Inclusion criteria for this phase of the study were nurses who administer, or monitor patients who have received, procedural sedation and analgesia during a medical procedure.
+An invitation to participate with a link to an online survey was distributed through Interventional Nursing Council of the Cardiac Society of Australia and New Zealand, Australian College of Operating Room Nurses, Medical Imaging Nurses Association, Gastroenterological Nurses College of Australia, Thoracic Society of Australia and New Zealand Respiratory Nurses Special Interest Group, and the College of Emergency Nursing Australia.
 
@@
 Nurses who were undergoing a one-day procedural sedation education session delivered by one of the authors (JS) were invited to participate.
+The course involved pre reading, based on previously described Minimum Standards for Safe Procedural Sedation (<https://www.aci.health.nsw.gov.au/resources/anaesthesia-perioperative-care/sedation/safe-sedation-resources>).
+The face-to-face teaching included practical examples for risk assessment, airway management, team communication and behaviours including graded assertiveness, and crisis management and escalation.
 
@@
 Items were chosen based on the authors' clinical experience as well as from clinical practice guidelines for procedural sedation [@apfelbaum2018practice; @Conway_2014; @conway2013; @conway2013a; @sutherland2020].
-Each item was prefixed with the phrase, 'I am confident I am able to...\".
+Each item was prefixed with the phrase, 'I am confident I am able to...".
 Responses were measured on a 7-point scale, ranging from 'strongly disagree' to 'strongly agree'.
 
-The initial bank of items for the NC-MSCS were assessed for relevance using a 4-point scale (1=not relevant; 2=somewhat relevant; 3=quite relevant; 4=highly relevant).
+The expert panel assessed the initial bank of NC-MSCS items for relevance using a 4-point scale (1=not relevant; 2=somewhat relevant; 3=quite relevant; 4=highly relevant).
 In addition, there was free-text space for the expert panel participants to provide suggestions to increase clarity of the wording of the items and to suggest additional items.
@@
 In addition to the NC-MSCS, participants responded to a set of items designed to ascertain the extent of their experience and education in aspects related to the management of sedation-related complications.
-Participants were also asked to rate the extent to which their overall knowledge and confidence changed from before to after the sedation training, using a 7-point rating scale from (1) greatly decreased to (7) greatly increased.
+Participants were also asked to rate the extent to which their overall knowledge and confidence changed from before to after the sedation training, using a 7-point rating scale from greatly decreased (1) to greatly increased (7).
 
@@
 Items with a content validity index of less than 0.78 were considered for revision and those with very low index values were considered for deletion[@Polit_2007].
+Scale-level content validity index was also calculated by averaging across items [@polit2006].
 In addition, the research team revised the wording of items based on panel members' responses regarding the clarity of items.
@@
 To evaluate responsiveness, analyses focused on testing the hypothesis that there would be a positive correlation between the change in participants NC-MSCS scores and changes in participant ratings of their overall knowledge and confidence in managing sedation complications from before to after undertaking a training course in sedation.
-Linear regression was used to determine the association between total NC-MSCS scores with participants' ratings of overall knowledge and confidence in managing PSA complications as well as change in knowledge and confidence from pre to post training in sedation and general self-efficacy scale scores.
+Linear regression was used to determine the association between the change in NC-MSCS scores from pre to post training and the extent to which participants' perceied their overall knowledge and confidence in managing PSA complications had changed.
 We used Tufte Slopegraph to visually display the change in NC-MSCS scores from the pre to post time-points, and used bootstrap estimation (5000 resamples) to calculate the mean difference with 95% confidence intervals [@ho2019].
@@
 Demographic characteristics are presented in Table \@ref(tab:tab1).
-The majority of the sample was highly experienced both in terms of total years in nursing and the number of years experience with procedural sedation.
+The majority of the sample was highly experienced both in terms of total years in nursing and the number of years of experience with procedural sedation.
 
@@
 Examination of the scree plot (Figure \@ref(fig:scree)) and parallel analysis indicated that a 3-factor solution was appropriate.
-Items that did not meet criteria were deleted one at a time with factor analyis repeated after each item deletion.
+Items that did not meet criteria were deleted one at a time with factor analysis repeated after each item deletion.
 We repeated this process until all items retained had a factor loading of at least 0.40 and loaded on one coherent factor.
@@
 
-A total of `r nrow(targets::tar_read(resp_change))` participated in the pre-test post-test study.
+A total of `r nrow(targets::tar_read(resp_change))` nurses participated in the pre-test post-test study.
 Characteristics for participants included in this phase of the study are displayed in Table \@ref(tab:resptable).
@@
 A large sample of nurses with diverse clinical experience across the numerous specialties in which sedation is frequently used participated in the study.
-This provided the opportunity to eliminate redundancy from an inital comprehensive item pool, which was created by the authors of this study but refined by an expert panel using a rigorous process for establishing content validity [@Polit_2007].
+This provided the opportunity to eliminate redundancy from an initial comprehensive item pool, which was created by the authors of this study but refined by an expert panel using a rigorous process for establishing content validity [@Polit_2007].
 The resultant 18-item NC-MSCS demonstrated a robust 3-factor structure with high internal consistency overall, as well as for each subscale measuring the domains of confidence in risk assessment, identification and responses to cardiorespiratory complications and application of airway interventions.
@@
 
-The NC-MSCS does not attempt to measure overcomplicated activities or tasks that go beyond nurses' knowledge or competences related to administering and monitoring procedural sedation, which have been outlined in clinical practice guideline statements from professional societies [@apfelbaum2018practice; @conway2013].
+The NC-MSCS does not attempt to measure over-complicated activities or tasks that go beyond nurses' knowledge or competences related to administering and monitoring procedural sedation, which have been outlined in clinical practice guideline statements from professional societies [@apfelbaum2018practice; @conway2013].
 The 18-item NC-MSCS offers a very quick and simple tool for measuring self-efficacy in performing such aspects of procedural sedation management.
-Although no prior research has specifically examined the effect of low levels on confidence toward the optimal management of sedation-related complications, research from other similar clinical contexts provides some insight.
+Although no prior research has specifically examined the effect of low levels of confidence toward the optimal management of sedation-related complications, research from other similar clinical contexts provides some insight.
 For example, research in the resuscitation context has consistently demonstrated that lack of confidence is a barrier to achieving good quality cardiopulmonary resuscitation [@vaillancourt2013; @roh2012].
@@
 Although the potential for a ceiling effect should not be ruled out, it is reassuring that the distribution of scores in the pre-sedation training group was not right-skewed.
-It is likely the higher ratings for items within these particular subscales that were observed in the online survey were associated with specific characteristics of the sample, such as participants' years of experience in nursing and the clinical settings in which the participants practiced (e.g.
-critical care setting versus procedural/medical settings).
+It is likely the higher ratings for items within these particular subscales that were observed in the online survey were associated with specific characteristics of the sample, such as participants' years of experience in nursing and the clinical settings in which the participants practiced (e.g. critical care setting versus procedural/medical settings).
 
@@
 The sample for the online survey was highly experienced and reported high levels of confidence in managing sedation complications.
-A convenience sampling approach and recruitment of participants through professional nursing organizations is the likely reason for.
+A convenience sampling approach and recruitment of participants through professional nursing organizations is the likely cause.
 The sample is therefore not entirely representative of the broader population of nurses who are involved in the management of procedural sedation.
@@
 
-In many institutions, considerable time and effort is directed towards annual compentency assessments for a variety of aspects of clinical care.
+In many institutions, considerable time and effort is directed towards annual competency assessments for a variety of aspects of clinical care.
 Competency in procedural sedation is one such area.
-The timeframe for such assessments, however, seems to be arbitrarily set and there is limited consideration of tailoring assessment to nurses individual capabilitlies and education needs.
+The timeframe for such assessments, however, seems to be arbitrarily set and there is limited consideration of tailoring assessment to nurses individual capabilities and education needs.
 Application of the NC-MSCS in education practice could be useful as a tool to stratify more experienced nurses to receive either further education and training in sedation (low confidence) or straight to simulation testing to ensure inaccurate calibration (high confidence but poor performance) is not an issue.
@@
 We recommend future testing of the NC-MSCS in samples with greater heterogeneity.
-The use of a professional organisations gives rise to selection bias.
 A convenience sampling approach was used for the pre-test post-test study.
 As such, selection bias may have influenced the results of the analyses conducted to evaluate the responsiveness of the NC-MSCS.
-Further psychometric testing to establish criterion-related validity and test--retest reliability would strengthen confidence in the usefullness of the NC-MSCS.
+Further psychometric testing to establish criterion-related validity and test--retest reliability would strengthen confidence in the usefulness of the NC-MSCS.
 
@@
 targets::tar_read(ncmscs_plot)
+
 ```

### 2020-09-02 R/comb_dist_plot.R

@@ -1,0 +1,17 @@
+#' Combine distribution plots
+#' @export
+#' @importFrom patchwork plot_layout plot_annotation
+#' @importFrom ggplot2 theme_classic
+make_comb_dist_plot <- function(risk_dist,
+                                cardioresp_dist,
+                                airway_dist,
+                                ncmscs_total_dist) {
+  comb <- risk_dist /
+    cardioresp_dist /
+    airway_dist /
+    ncmscs_total_dist
+
+  comb +
+    plot_annotation(tag_levels = "A")&
+    theme_classic()
+}

### 2020-09-02 R/keys.R

@@ -1,0 +1,32 @@
+#' Keys
+#' @export
+#'
+
+keys <- function() {
+  list(
+    risk = c(
+      "RiskHistory",
+      "RiskOSA", "DifficultIntubate", "DifficultBMV",
+      "RiskASA", "RiskBMI", "RiskCardioresp"
+    ),
+    cardioresp = c(
+      "IdentifyRespRate",
+      "IdentifyBradycardia", "IdentifyHypotension", "RespondHypoventilation",
+      "RespondHypoxia", "RespondBradycardia", "RespondHypotension"
+    ),
+    airway = c(
+      "OPA", "NPA", "JawSupport",
+      "ChinLift"
+    ),
+    ncmscs_total = c(
+      "RiskHistory",
+      "RiskOSA", "DifficultIntubate", "DifficultBMV",
+      "RiskASA", "RiskBMI", "RiskCardioresp",
+      "IdentifyRespRate",
+      "IdentifyBradycardia", "IdentifyHypotension", "RespondHypoventilation",
+      "RespondHypoxia", "RespondBradycardia", "RespondHypotension",
+      "OPA", "NPA", "JawSupport",
+      "ChinLift"
+    )
+  )
+}

### 2020-09-02 R/make_dist_plot.R

@@ -1,0 +1,18 @@
+#' @title
+#' @return
+#' @export
+#' @importFrom ggplot2 ggplot aes
+#' labs geom_histogram
+#' @importFrom glue glue
+make_dist_plot <- function(data, scale, xaxis) {
+  {{ data }} %>%
+    ggplot(aes(x = {{ scale }})) +
+    geom_histogram(
+      binwidth = 0.5,
+      fill = "#2a6ebb"
+    ) +
+    labs(
+      y = "Count",
+      x = glue::glue("{xaxis}")
+    )
+}

### 2020-09-02 R/scree_plot.R

@@ -6,7 +6,7 @@
 #' @importFrom tidyr pivot_longer
 #' @importFrom dplyr select
 #' @importFrom  ggplot2 aes ggplot geom_line geom_point theme element_blank
-#'
+#' theme_classic
 scree_plot <- function(ncmscs_items) {
   polycor <- polychoric(as.matrix(ncmscs_items), smooth = FALSE)
   ev <- eigen(cor(polycor$rho))
@@ -27,5 +27,8 @@ scree_plot <- function(ncmscs_items) {
     ggplot(aes(y = Eigenvalues, x = Components, color = type)) +
     geom_line() +
     geom_point() +
-    theme(legend.title = element_blank())
+    theme_classic()+
+    theme(legend.title = element_blank(),
+          legend.position = "top")
+
 }

### 2020-09-11 _targets.R
lower case

@@ -223,7 +223,7 @@ tar_pipeline(
       ) %>%
       gtsummary::italicize_levels()
   ),
-  tarchetypes::tar_render(manuscript, "manuscript.Rmd"),
+  tarchetypes::tar_render(manuscript, "manuscript.rmd"),
   tar_target(risk_dist, make_dist_plot(
     ncmscs_df, risk,
     xaxis = "Risk assessment subscale"

### 2020-09-14 manuscript.rmd
dockerfile
submitted to jcn

@@
 bibliography: Extras/references.bib
-csl: Extras/harvard.csl
+csl: Extras/apa.csl
 output:
@@
 ```
+
+## Declarations
+
+Availability of data and material (data transparency): All data used is available [here](https://github.com/awconway/nc-mscs).
+
+Code availability: Code to reproduce the analyses is available [here](https://github.com/awconway/nc-mscs).
+
+Abbreviated title: Nursing confidence in managing sedation complications scale
+
+Funding statement: Support was provided solely from institutional and/or departmental sources.
+
+Conflicts of interest: The authors declare no competing interests.
+
+Author contributions: AC: Study design, data analysis and wrote manuscript; KC: Revised the manuscript for important intellectual content; NK: Revised the manuscript for important intellectual content; JS: Study design, data collection, revised the manuscript for important intellectual content.
 
@@
 
+## Impact statement
+
+What does this paper contribute to the wider global clinical community?
+
+-   The psychometric properties of the NC-MSCS appear encouraging.
+It could be a useful tool for self-reflection, or to guide and inform sedation training initiatives and to inform formal competency assessment activities.
+-   The 18-item NC-MSCS offers a very quick and simple tool for measuring self-efficacy in performing aspects of procedural sedation management.
+-   An online version of the complete scale can be accessed and scored [here](https://nc-mscs.netlify.app/).
+
 Keywords: deep sedation, conscious sedation, patient safety, self-efficacy, nursing, scale development, item response theory
-
-\pagebreak
-
-## Declarations
-
-Availability of data and material (data transparency): All data used is available [here](https://github.com/awconway/nc-mscs).
-
-Code availability: Code to reproduce the analyses is available [here](https://github.com/awconway/nc-mscs).
-
-Abbreviated title: Nursing confidence in managing sedation complications scale
-
-Funding statement: Support was provided solely from institutional and/or departmental sources.
-
-Conflicts of interest: The authors declare no competing interests.
-
-Author contributions: AC: Study design, data analysis and wrote manuscript; KC: Revised the manuscript for important intellectual content; NK: Revised the manuscript for important intellectual content; JS: Study design, data collection, revised the manuscript for important intellectual content.
 
@@
 Therefore, prompt detection and treatment of sedation-related complications is vital to ensure patient safety during procedures performed with PSA [@Bhananker_2006].
+
+## Background
 
@@
 In the third phase, responsiveness was evaluated using a pre-test post-test design.
+Ethical approval was provided by the Queensland University of Technology Human Research Ethics Committee (61986 and 56161).
 
@@
 #### Statistical methods
+
+All analyses were conducted using R [@Rcore] and code to reproduce the analyses is available [here](https://github.com/awconway/nc-mscs).
 
@@
 
-The NC-MSCS does not attempt to measure over-complicated activities or tasks that go beyond nurses' knowledge or competences related to administering and monitoring procedural sedation, which have been outlined in clinical practice guideline statements from professional societies [@apfelbaum2018practice; @conway2013].
-The 18-item NC-MSCS offers a very quick and simple tool for measuring self-efficacy in performing such aspects of procedural sedation management.
-Although no prior research has specifically examined the effect of low levels of confidence toward the optimal management of sedation-related complications, research from other similar clinical contexts provides some insight.
-For example, research in the resuscitation context has consistently demonstrated that lack of confidence is a barrier to achieving good quality cardiopulmonary resuscitation [@vaillancourt2013; @roh2012].
-Therefore, the NC-MSCS could be a useful tool for self-reflection, or to guide and inform sedation training initiatives and to inform formal competency assessment activities.
-An online version of the complete scale can be accessed and scored [here](https://nc-mscs.netlify.app/).
-
 The right-skewed distribution of subscale scores in the online survey should be noted.
@@
 It is likely the higher ratings for items within these particular subscales that were observed in the online survey were associated with specific characteristics of the sample, such as participants' years of experience in nursing and the clinical settings in which the participants practiced (e.g. critical care setting versus procedural/medical settings).
-
-<!--# The factor structure identified through exploratory factor analysis did not exactly align with the conceptual framework we used to create the initial bank of items.
-The bank of items was constructed with a tentative 4-domain structure, whereas parallel analysis indicated a 3-factor structure was the most parsimonious solution.
--->
 
@@
 Conducting confirmatory factor analysis with a different sample of nurses would be useful to determine if the factor structure we identified is robust to sampling procedures.
-
-<!--# The risk assessment and identification/responses to cardiorespiratory complications factors explained a considerably percentage of variance than the factor containing items related to technical airway skills.
-Different patient characteristics in the responsiveness study.
--->
 
@@
 
-In many institutions, considerable time and effort is directed towards annual competency assessments for a variety of aspects of clinical care.
-Competency in procedural sedation is one such area.
-The timeframe for such assessments, however, seems to be arbitrarily set and there is limited consideration of tailoring assessment to nurses individual capabilities and education needs.
-Application of the NC-MSCS in education practice could be useful as a tool to stratify more experienced nurses to receive either further education and training in sedation (low confidence) or straight to simulation testing to ensure inaccurate calibration (high confidence but poor performance) is not an issue.
-
 ### Limitations
@@
 
-### Conclusion
+## Conclusion
 
@@
 This scale could be used to guide and inform education and training of nurses as well as complement formal competency assessment.
+
+## Relevance to clinical practice
+
+The NC-MSCS does not attempt to measure over-complicated activities or tasks that go beyond nurses' knowledge or competences related to administering and monitoring procedural sedation, which have been outlined in clinical practice guideline statements from professional societies [@apfelbaum2018practice; @conway2013].
+The 18-item NC-MSCS offers a very quick and simple tool for measuring self-efficacy in performing such aspects of procedural sedation management.
+Although no prior research has specifically examined the effect of low levels of confidence toward the optimal management of sedation-related complications, research from other similar clinical contexts provides some insight.
+For example, research in the resuscitation context has consistently demonstrated that lack of confidence is a barrier to achieving good quality cardiopulmonary resuscitation [@vaillancourt2013; @roh2012].
+Therefore, the NC-MSCS could be a useful tool for self-reflection, or to guide and inform sedation training initiatives and to inform formal competency assessment activities.
+An online version of the complete scale can be accessed and scored [here](https://nc-mscs.netlify.app/).
+Also of note, considerable time and effort is directed in many hospitals towards annual competency assessments for a variety of aspects of clinical care.
+Competency in procedural sedation is one such area.
+The timeframe for such assessments, however, seems to be arbitrarily set and there is limited consideration of tailoring assessment to nurses individual capabilities and education needs.
+Application of the NC-MSCS in education practice could be useful as a tool to stratify more experienced nurses to receive either further education and training in sedation (low confidence) or straight to simulation testing to ensure inaccurate calibration (high confidence but poor performance) is not an issue.
+Further research would be required to evaluate the efficacy of this approach.
 

### 2020-09-21 manuscript.rmd
nursing open

@@
 
-### Introduction
+### Aim
 
-It is possible that nurses may not take actions to manage sedation-related complications if they lack confidence in their abilities to complete the necessary tasks.
-The aim of this study was to develop the Nursing Confidence in Managing Sedation Complications Scale (NC-MSCS).
+To develop the Nursing Confidence in Managing Sedation Complications Scale (NC-MSCS).
+
+### Design
+
+A multi-phased approach was used to inspect the psychometric properties of the scale.
 
@@
 
-An expert panel rated the relevance of an initial bank of items.
-Items with a content validity index of less than 0.78 were revised or deleted.
-An online survey containing items from the revised scale was distributed to nurses who were members of five different specialty nursing associations in Australia.
-Principal axis factoring and promax rotation was used for factor extraction.
-Multivariable linear regression was used to identify associations between scale scores and nurses' experience and education regarding sedation.
-Internal consistency was calculated to examine reliability.
-Responsiveness was evaluated using a pre-test post-test design with a sample of nurses who completed a sedation education program.
+Content validity was assessed by an expert panel.
+Exploratory factor analysis was used for item reduction and multivariable linear regression was used to explore construct validity.
+Responsiveness was evaluated using a pre-test post-test design.
 
@@
 Responses from 228 nurses who participated in the online survey were analysed.
-An 18-item, 3-factor solution was identified as the most parsimonious solution, with subscales accounting for 65.6% of the variance.
+An 18-item, 3-factor solution was identified, with subscales accounting for 66% of the variance.
 Cronbach's alpha for the scale (`r round(targets::tar_read(reliability_total)$total$std.alpha, 2)`) and subscales was high (\>0.85).
-There were significant differences (p\<0.001) in NC-MSCS scores relative to years of nursing experience and work environment (critical care/anaesthesia versus procedural/operating theatre).
-The change in NC-MSCS scores reported by the 31 nurses who participated in the pre-test post-test study increased significantly from before to after sedation training (mean difference = `r glue::glue("{round(targets::tar_read(paired_diff)$result$difference, 1)}; 95% CI = {round(targets::tar_read(paired_diff)$result$pct_ci_low, 1)}-{round(targets::tar_read(paired_diff)$result$pct_ci_high, 1)}")`).
-Change in NC-MSCS was correlated with the change in overall confidence and knowledge about managing sedation complications.
-
-### Conclusion
-
-The NC-MSCS is a valid and reliable instrument, which could be used to guide and inform sedation training programs and competency assessments.
+There were significant differences (p\<0.001) in NC-MSCS scores relative to years of nursing experience and work environment.
+NC-MSCS scores from a sample of 31 nurses increased significantly from before to after sedation training (mean difference = `r glue::glue("{round(targets::tar_read(paired_diff)$result$difference, 1)}; 95% CI = {round(targets::tar_read(paired_diff)$result$pct_ci_low, 1)}-{round(targets::tar_read(paired_diff)$result$pct_ci_high, 1)}")`).
 
@@
 In the third phase, responsiveness was evaluated using a pre-test post-test design.
-Ethical approval was provided by the Queensland University of Technology Human Research Ethics Committee (61986 and 56161).
+The STROBE checklist was used to guide the reporting of results.
 
@@
 A standardized response mean (mean change divided by the standard deviation of the change score) was also calculated.
+
+### Ethics
+
+Ethical approval was provided by the Queensland University of Technology Human Research Ethics Committee (61986 and 56161).
 

### 2020-10-20 R1/R1.Rmd
revision submitted

---
toname: Nursing Open
toaddress: Editorial Board
opening: To the editor, 
closing: Regards,
spacing: 1
output: ConwayLetterTemplate::letter
---

Thank you for allowing us to revise our manuscript for further consideration for publication. Please find our responses to the comments from the reviewers below.

# Reviewer 1

*In this study, an instrument measuring nursing confidence in managing sedation complications was developed and validated. The paper English language is well. In my opinion, this is a well-written manuscript that needs few corrections or clarification.*

>Thank you for reviewing our manuscript.

## Abstract

*Methods: Please mention how items were generated.*

>We have added the following sentence to the methods:

>'An initial bank of items was created based on the authors’ experience and clinical practice guidelines.'

## Methods

*How many experts did participate in this phase?*

>We reported that 9 participants were included in the content validity process in the results section (content validity section page 11).

*I highlighted a spelling error on page 10.*

>Corrected

*Pre-test post-test study page 8: How does this question (Participants were also asked to rate the extent to which their overall knowledge and confidence changed from before to after the sedation training, using a 7-point rating scale from greatly decreased (1) to greatly increased) help in the process of the scale development?*

>This question was used to evaluate responsiveness, as reported in the statistical analysis section (last paragraph page 10):

>'To evaluate responsiveness, analyses focused on testing the hypothesis that there would be a positive correlation between the change in participants NC-MSCS scores and changes in participant ratings of their overall knowledge and confidence in managing sedation complications from before to after undertaking a training course in sedation.'

## Results

*The internal consistency of the scale and its subscales should be mentioned.*

>We reported the Cronbach’s alpha coefficient in the results section - page 12.

*Please explain why you did not exclude those who never administer or monitor patients who have received procedural sedation from the study.*

>We have included a statement to justify inclusion of these participants in the limitations section where we address the potential for selection bias:

>'A small number of participants in the online survey reported that they would not administer or monitor patients who have received procedural sedation in a typical working week. We chose not to exclude these patients from the analyses because it is possible that they did have experience using procedural sedation, but just do not currently use it during a typical working week.'

# Reviewer 2

*is good for assess*

>Thank you for reviewing our manuscript.
